Capstone Movielens Report

### 2025-02-03 reports/capstone-movielens-report.Rmd
Backref citation sample 2

---
title: "Capstone Movielens Report"
author: "Azamat Kurbanaev"
date: "`r Sys.Date()`"
#bibliography: references.bib
#csl: bit-numerical-mathematics.csl 
output:
  pdf_document: 
    df_print: paged
    toc: true
    fig_caption: true
    keep_tex: true
    #citation_package: biblatex

@@

**References**

\addcontentsline{toc}{section}{References}
 \color{black}
\bibliography{references}
\bibliographystyle{mla-good}

>>>>

---
title: "Capstone Movielens Report"
author: "Azamat Kurbanaev"
date: "`r Sys.Date()`"
output:
  pdf_document: 
    df_print: paged
    toc: true
    fig_caption: true
    keep_tex: true

@@

\addcontentsline{toc}{section}{Whole References}
\bibliography{references}
\bibliographystyle{mla-good}
